---
title: "Regression Models Project"
output: word_document
---

# Executive Summary
Motor Trend, a magazine about the automobile industry is interested in exploring the relationship between a set of variables and miles per gallon (MPG). They are particularly interested in the following two questions:

- Is an automatic or manual transmission better for MPG
- Quantifying how different is the MPG between automatic and manual transmissions?

We will do first some exploratory analysis and then come up with a model to answer this questions. An analysis of th residuals and errors will be also developed.

# Is an automatic or manual transmission better for MPG
We are going to check hoy the mpg varies for the manual and automatic transmission. For that the boxplot is very useful:

```{r boxplot}
data=mtcars
boxplot(data$mpg~data$am,main="MPG per transmission type",xlab="Transmission type",ylab="MPG",col=terrain.colors(2))
legend("topleft",inset=0.05,title="Tranmission type",c("Manual","Automatic"),fill=terrain.colors(2))
```

As we can see, the median and at least 50% of the points for each type lie separate, so we can say that manual transmission has less MPG than automatic in general. This is enough to answer the question for a generic car. This result makes sense because automatic transmission is designed not only to make life easier for the driver but also to improve the efficiency of the driving.

# Quantifying how different is the MPG between automatic and manual transmissions?
Let's try to build a linear regression model to check how much mpg in average has each type of transmission. After some explatory analysis and backward feature selection we selected the following linear model:
```{r exploratory, results='hide'}
#Results shown in appendix
#pairs(~mpg+qsec+wt+am,data)
```
```{r model,results='hide'}
#Backward feature selection. Hide the results because of the 2-page limit
model = step(lm(mpg~.,data),direction = "backward")
```
The features selected are and the confidence intervals for the model parameters are:
```{r features}
model$coefficient
confint(model,"am",level = 0.95)
```
The residuals are:
```{r residuals,results='hide'}
#Result shown in appendix due to space requirements
#plot(predict(model),resid(model))
#abline(h=mean(resid(model)),col="red")
```
The residuals are unbiased and homoscedastic (see appendix).

In conlcusion: changing from manual to automatic increases the MPG in average 2.936 mpg, being therefore a more efficient transmission. One drawback is that because "am" is a binary variable the lm doesnt regress very good, being then necessary to include more variables. One effect is the loss in significance but a higher R^2.

#Appendix
## Exploratory analysis:
```{r}
#Check linearity in variables that we want to use
pairs(~mpg+qsec+wt+am,data)
```
## Summary of the model selection and model selected:
```{r}
#Step by step computation and selection of features
step(lm(mpg~.,data),direction = "backward")
#Summary of the model selected (higher R^2 but am not tht significant)
summary(model)
```
## Analysis of the residuals:
```{r residuals2}
par(mfrow=c(2,2))
plot(model)
```
